---
title: "Homework 1, Econ B2000"
author: 'Christopher Tinevra, Group Members: Isabela Vieira, Akimawe Kadiri, Nicole
  Kerrison, Mostafa Ragheb '
date: "9/14/2020"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

### Question 3: "Simulating a Dice Roll"

Theoretical probability of roll - the expectation is to roll a 6 on a dice of 6 sides for at least once 1/36= (.02778)

In order to create a fair dice simulation in R. We first  begin by creating a variable called dice rolls and set the size to 2 representing the utilization of 2 dice and any time we roll we want replacements of numbers.

```{r}
die.rolls <- function (){
  dice <- sample(x=1:6, size = 2, replace = TRUE)}

```

Then we want to create a simulation that runs this at least 20 times

```{r}
simtrial <- replicate(20,die.rolls())
```

Then create a table to of the simulation once its complete.

```{r}
table(simtrial)
```

#Then generate the frequency of the outcome and plot the data

Frequency - this is the % of times we virtually rolled the numbers below

```{r}
table(simtrial)/length(simtrial)
```

Plot - This plots the number of times in the simulation roll that we record a number 

```{r}
plot(table(simtrial), xlab = 'Dice number', ylab = 'Frequency', main = '20 Rolls of 2 Fair Dice')
```

### Question 4: "Replication of Lecture 1 Rstudio notes"

```{r}
load("acs2017_ny_data.RData")
acs2017_ny[1:10,1:7]
attach(acs2017_ny)
```
```{r}
summary(acs2017_ny)
print(NN_obs <- length(AGE))
```
Sample size for this database equates to `r prettyNum(NN_obs, big.mark = ",")`

```{r}
summary(AGE[female == 1])
summary(AGE[!female])
```

```{r}
mean(AGE[female == 1])
sd(AGE[female == 1])
mean(AGE[!female])
sd(AGE[!female])
```

Women in this dataset are, on average, a bit older, with an average age of `r round(mean(AGE[female == 1]), digits = 1)` compared with `r round(mean(AGE[female != 1]), digits = 1)` for men. 

```{r}
summary(EDUC[female == 1])
summary(EDUC[!female])
```

```{r}
mean(educ_college [female == 1])*100
mean(educ_college [!female])*100

```
From the database, I found interesting that the education level between female and male seems to be equally distributed. For example: attendance for college education for women have an average percentage of `r mean((educ_college [female == 1])*100)`% in comparison to the average percentage of `r mean((educ_college [!female])*100)`% for men. Overall, it appears that the database shows that both gender dont have high attendance for college education.

### Question 5: "S&P 500 Index"

```{r}
options(readr.num_columns = 0)
setwd("~/Library/Mobile Documents/com~apple~CloudDocs/Economics Master/Econometrics/HW_1_R_markdown_files")
library(readr)
S_P_Stock_Price <- read_csv("S&P 500 Index Price.csv")
```

Calculating the returns on the S&P with the data imported in R

Table below illustrates the first values at the beginning of the month for the S&P 500

```{r}
head(S_P_Stock_Price)
```

Table below shows the adj close numbers of the S&P 500 Index

```{r}
S_P_Stock_Price[1:30, "Adj Close"]
```

We want to isolate the adj close values of the s&p in order to calculate returns by creating a new variable with just the adjusted close prices

```{r}
sp_pricedate <-S_P_Stock_Price[, "Date", drop = FALSE]
sp_pricenew <-S_P_Stock_Price[, "Adj Close", drop = FALSE]
cbind(sp_pricedate,sp_pricenew)
```

Calculating Adj Close Returns 

```{r}
n <-nrow(sp_pricenew)
sp_returns <- log(sp_pricenew[2:n,1])-log(sp_pricenew[1:(n-1),1])
returns <- sp_returns*100
summary(returns)
xdate <- sp_pricedate[2:21,"Date"]
df1 <- cbind.data.frame(xdate,returns)
#A new data frame will be created to reflect the Adj.Close Returns for S&P500 with each date
print(df1)
```
